Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
explain for node_contents

>>>>

\than{I put an explanation for $\mathsf{node\_contents}(\texttt{n}, \cdot , \mathsf{range})$ here }

The expression $\mathsf{node\_contents}(\texttt{n}, \cdot , \mathsf{range})$  signifies that \texttt{n} points are being directed towards an empty leaf node. On the other hand, the expression $\mathsf{node\_contents}(\texttt{n}, (\mathsf{k}, \mathsf{v}), \mathsf{range})$ denotes that \texttt{n} points are directed towards a node, which houses the key $\mathsf{k}$ and its corresponding value $\mathsf{v}$.
